#Practical Machine Learning Final Project

##Objective

The object of this project is to predict how well the users perform barbells.

##Load the data

```{r cache = TRUE}
setwd("d:/coursera/practical ML/project")
library(caret)
training <- read.csv("pml-training.csv", na.strings = c("", NA))
testing <- read.csv("pml-testing.csv", na.strings = c("", NA))
```

##Cleaning data

I remove the features in testing data set that are all NAs and the first 5 columns since they
are related to time and the last one which is problem id

```{r}
problemid <- testing$problem_id
features <- names(testing[, colSums(is.na(testing)) == 0])
##remove the first 7 and the last
features <- features[8 : 59]
testing <- testing[, features]
```

I select the training data features according to the testing set

```{r}
classes <- training$classe
training <- training[, features]
training <- cbind(classes, training)
```

##Do the classification

Split the training data into training and test set

```{r}
intrain <- createDataPartition(y = training$classes, p = 0.7, list = FALSE)
training <- training[intrain, ]
testing1 <- training[-intrain, ]
```

###First use the boosting

```{r, cache = TRUE}
set.seed(12345)
fitControl <- trainControl(method = "repeatedcv",
                           number = 5,
                           repeats = 1)
modgbm <- train(classes~., data = training, method = "gbm",
                trControl = fitControl,
                verbose = FALSE)
predgbm <- predict(modgbm, newdata = testing1)
confusionMatrix(predgbm, testing1$classes)
```

###Then I use the classification tree

```{r cache = TRUE}
set.seed(12345)
modtree <- train(classes~., data = training, method = "rpart")
predtree <- predict(modtree, newdata = testing1)
confusionMatrix(predtree, testing1$classes)
```

###Then I use the linear discriminant analysis

```{r cache = TRUE}
set.seed(12345)
modlda <- train(classes~., data = training, method = "lda")
predlda <- predict(modlda, newdata = testing1)
confusionMatrix(predlda, testing1$classes)
```

##Finally I predict the outcome in the testing data set

```{r}
predictions <- predict(modgbm, newdata = testing)
results <- data.frame(problemid, predictions)
results
```

